---
title: "Multiscale Graph Correlation"
date: "April 20, 2016"
output: html_document
---

# ``R`` Functions

```{r echo=FALSE, message =FALSE, warning = FALSE}
library(igraph)
library(RefManageR)
library(xtable)
library(grid)
library(ggplot2)
library(png)
library(grid)
bib <- ReadBib(system.file("Bib", "biblatexExamples.bib", 
                           package = "RefManageR"), check = FALSE)
BibOptions(check.entries = FALSE, style = "markdown", bib.style = "alphabetic", cite.style = 'alphabetic')
```

## Permutation Tests

```{r}
# disToRank - compute a rank of a distance matrix
# LocalGraphCorr - calculate local graph correlation
# PermutationTest - prints out pvalues of independence tests for two distance matrix
```

- A function ``PermutationTest`` sometimes returns a really small negative pvalues(e.g.  -6.661338e-16). 

- What is a difference between ``PermutationTest(C, P, rep, allP, option)`` and ``CorrPermDistTest(type, rep, cv, titlechar, allP, option)`` ? 

- Why we need bootstrap samples to use for neighborhood validation? 


## Pvalue Heatmap

```{r}
elegans <- read.graph("../data/c.elegans.herm_pharynx_1.graphml", format = "graphml")
A <- get.adjacency(elegans)
A <- as.matrix(A) # it is not symmetric
A <- ifelse(A > 1, 1, A)
dist.A <- ifelse(A == 1, 0, 1)
dist.A2 <- shortest.paths(elegans, v = V(elegans), to = V(elegans), mode="all", weights = NULL, algorithm = "dijkstra")
# univariate distance matrix
uni.dist <- function(vec){
  n <- length(vec)
  mat <- matrix(0, n, n)
  for(i in 1:(n-1)){
    for(j in (i+1):n){
      mat[i,j] <- sqrt((vec[i] - vec[j])^2)
      mat[j,i] <- mat[i,j]
    }
  }
  return(mat)
}
soma_pos <- V(elegans)$soma_pos # continuous variable
soma.dist <- uni.dist(soma_pos) # distance matrix of soma position
# soma.A.B <- PermutationTest(dist.A, soma.dist, 500, 0, c(1,1,1,1)) 
# pvalue.A.sim <- soma.A.B[[2]]
# heatmap.2(pvalue.A.sim, dendrogram='none', Rowv=FALSE, Colv=FALSE,trace='none',
#          xlab = "Neighborhood Choice of A", labRow = "", labCol = "",
#          ylab = "Neighborhood Choice of B",  
#          main = expression("dcorr pvalue " ~ H[0] ~" : " ~ f[A*B] ~" = " ~f[A]*f[B]))

```


- Do you have any suggestions for drawing ``heatmap.2``? I want consistent gradient coloring, i.e. red when p-values = 0, and white when p-value = 1. (with legend included).

- Interpretation of p-value heatmap.

```{r}
PAD <- readPNG("../figure/P_A_D.png")
grid.raster(PAD)
```


Regarding neighborhood choice of $D$(cell direction), choosing only nearby neighbors results in (slightly) larger p-values; while for $A$ (neuronal network of c.elegans), including up to certain level of neighbors might lead to insignificant result.




```{r}
PAC <- readPNG("../figure/P_A_C.png")
grid.raster(PAC)
```


Variation in p-values is more dependent on neighborhood choice of $A$(neuronal network) than that of $C$(cell type). (It might imply that in local test, choosing more than the certain level of neighbors in neuronal connectivity network ensures rejecting null hypothesis) 




## Power Estimation

- Resampling method 

```{r}



```


- In case that a pair of data sets is available. 


- What is the benefit we can get through Multiscale Graph Correlation when we cannot find the optimal scale $(k^{*}, l^{*})$? 
